Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-15 WSSSPE4_report/wg_letters.tex
Address the open comments.

Scientists working on scientific software are often located in
disciplinary departments, depending on whether their software
originates from the mathematical, physical, chemical, or other
disciplines. As a consequence, they are frequently outside the core
areas of their science, and their contributions are typically to both
the research activity their software enables, as well as on
algorithm and implementation aspects. This presents issues when
letters of evaluation for hiring, tenure, and promotion do not specifically
cover how this is relevant to the discipline.%
\footnote{The extensive use of such letters, and the problems that are
  associated with it, may be an issue specific to the US.}

@@

\begin{itemize}
\item The Research Computing Association has produced a ``Dear Colleague'' letter on the issue. \katznote{add citation}
\item The National Science Foundation has produced a ``Dear Colleague'' letter that defines a ``product'' for the purposes of 2-page biosketches that does not include only publications, but also software. \katznote{add citation or link?}
\item The ACM published an article in the CACM (one of the co-authors
  was David Patterson) \katznote{why is Patterson significant here?} that explained that conference proceedings are
  \textit{the} venue in Computer Science, and this has been used to
  convince deans and provosts of the value of these proceedings
  publications. This article may serve as a template for computational
  science.
\item There is also a 1995 report by the National Academies about
  Computer Science that addresses some of these issues, specifically
  on how writing software should be considered in comparison to more
  theoretical research. \katznote{add citation -- \url{https://www.nap.edu/catalog/2236/academic-careers-for-experimental-computer-scientists-and-engineers}}
\end{itemize}

>>>>

Scientists working on scientific software are often located in
disciplinary departments, depending on whether their software
originates from the mathematical, physical, chemical, or other
disciplines. As a consequence, they are frequently outside the core
areas of their science, and their contributions are typically to both
the research activity their software enables, as well as on
algorithm and implementation aspects. This presents issues when
letters of evaluation for hiring, tenure, and promotion do not specifically
cover how this is relevant to the discipline.%
\footnote{The extensive use of such letters, and the problems that are
  associated with it, may be an issue specific to the United States.}

@@

\begin{itemize}
\item The Computing Research Association has produced a ``Best
  practices memo'' on the issue \cite{PSU99}. Among other points,
  the memo also clarified that conference proceedings are
  \textit{the} venue in Computer Science, and this has been used to
  convince deans and provosts of the value of these proceedings
  publications. The article may serve as a template for computational
  science.
\item The National Science Foundation has produced a number of ``Dear
  Colleague'' letter that consider the issue of software and, taken
  together, define a ``product'' for the purposes of
  2-page biosketches in a way that does not include only publications, but also
  software.%
  \footnote{The most pertinent such letter is
    \href{https://www.nsf.gov/pubs/2014/nsf14059/nsf14059.jsp}{NSF
      14-059, ``Dear Colleague Letter - Supporting Scientific
      Discovery through Norms and Practices for Software and Data
      Citation and Attribution''}.}
  This definition is ultimately codified in the National Science
  Foundation's ``Proposal and Award Policies and Procedures Guide''
  (often abbreviated as GPG) which in 2013 renamed the
  ``Publications'' section of 2-page biosketches to ``Products'' (see
  Chapter II.C.2.f(i)(c)) and now explicitly allows software to be
  referenced in this section.
\item There is also a 1995 report by the National Academies about
  Computer Science that addresses some of these issues, specifically
  on how writing software should be considered in comparison to more
  theoretical research \cite{NRC-careers-94}. 
\end{itemize}
